### 2022-07-03 paper/main.tex
mostly done

\par While Urban Areas are an effective method of measuring the true sizes of cities, they are difficult to map and obtain statistics on. Their shapes are generally compact and do not have any sort of uniform, governing body. To alleviate these issues, we choose Metropolitan Statistical Areas (MSAs) as our scale. MSAs consist of the county or counties in which an Urban Area lies, alongside any counties in which 25\% of the population commutes to a core county (REF). In this way, we gain the population measurement accuracy of UAs with the ease of data access from state-defined municipalities. MSAs also lump together similar, nearby cities, such as New York, Newark, and Jersey City, to avoid redundant analysis. As of March 2020, there are 384 Metropolitan Statistical Areas (REF), each with a corresponding Reddit community.

\subsection{Geography and the Internet}

% TODO

@@

\par From the overlap data, we can see that crime is a frequent topic of discussion even outside the \texttt{nyc} subreddit for the identified crime posters. However, the overlap with several New York City-related communities indicates that many of the crime posters have some relation to the city itself.

\par While the two types of posters share some subreddits, their political community overlap is fairly different. To identify political subreddits, we derive the methodology from (REF). Table \ref{table:table-8} shows the political subreddits with the largest amount of overlap.

@@

\par Here, we see that the two groups diverge on political opinions. Those that post about crime trend more towards the right; \texttt{LockdownSkepticism} is a community critical of Covid-19 restrictions and \texttt{Conservative} is Reddit's largest right-leaning political community. Non-crime posters are active in politically moderate communities such as \texttt{tuesday} and \texttt{neoliberal}, as well as \texttt{VoteDem}, which supports the Democratic Party.

\par From our user-level analysis, we have identified several characteristics of crime posters. First, these users are consistently more negative than non-crime posting users. They post about crime frequently, as indicated by their significant overlap with crime discussion specific communities. However, they are often local to the communities in which they post, as they have significant overlap to location specific hobby and sport communities. Lastly, those that post about crime are more active in conservative political communities than those who don't post about crime.

@@

\par Through analysis of user-submitted posts, we have found that communities that represent larger Metropolitan Statistical Areas and more liberal Metropolitan Statistical Areas tend to have higher rates of crime discussion. However, there is no correlation between high documented crime rates and high crime discussion rates. Furthermore, we have found that the users that make submissions about crime are significantly more negative in their posting and commenting style than those that post about non-crime topics.

\par This paper presents an alternative approach to the measurement of crime discussion and media. While there have been several notable papers examining the relationship between crime discussion and traditional media, few have bridged the gap between media, such as newspapers and television stations, and modern social media networks, such as Reddit.

>>>>

\par While Urban Areas are an effective method of measuring the true sizes of cities, they are difficult to map and obtain statistics on. Their shapes are generally compact and do not have any sort of uniform governing body. To alleviate these issues, we choose Metropolitan Statistical Areas (MSAs) as our scale. MSAs consist of the county or counties in which an Urban Area lies, alongside any counties in which 25\% of the population commutes to a core county (REF). In this way, we gain the population measurement accuracy of UAs with the ease of data access from state-defined municipalities. MSAs also lump together nearby cities, such as New York, Newark, and Jersey City, to avoid redundant analysis. As of March 2020, there are 384 Metropolitan Statistical Areas (REF), each with a corresponding Reddit community.

\subsection{Geography and Social Media}

\par When analyzing our selected Reddit communities, we need to consider the geospatial aspects of social media. There is no barrier preventing someone from, for example, Los Angeles from posting in a New York City community. (REF) measure the nature of geographic social networks. They compared the geospatial proximity of graph-connected users on four social media sites. They found that sites, such as FourSquare, that had an explicitly nature had a higher degree of locality. However, sites that focused more on general information exchanges showed less geographic clustering. The Reddit communities we are analyzing hold an interesting space between these two categories; they are both tied to place and detached from it. There is not a geographic component stopping a user from posting to a distant community, but the geospatial nature of the community itself can lead to geographic clustering.

@@

\par From the overlap data, we can see that crime is a frequent topic of discussion even outside the \texttt{nyc} subreddit for the identified crime posters. However, the overlap with several New York City-related communities indicates that many of the crime posters have some relation to the city itself. When compared to non-crime posters, crime posters exhibit less of a sense of locality. Nine of the ten communities that non-crime posters have strong overlap with are explicitly related to New York City, while only seven of the ten communities that crime posters overlap with are geospatially defined.

\par While the two types of posters share some subreddits, their political community overlap is fairly different. To identify political subreddits, we derive the methodology from (REF - from jeremy). Table \ref{table:table-8} shows the political subreddits with the largest amount of overlap.

@@

\par Here, we see that the two groups diverge on political opinions. Those that post about crime trend more towards the right; \texttt{LockdownSkepticism} is a community critical of Covid-19 restrictions and \texttt{Conservative} is Reddit's largest right-leaning political community. Non-crime posters are active in politically moderate communities such as \texttt{tuesday} and \texttt{neoliberal}, as well as \texttt{VoteDem}, which supports the Democratic Party. Crime posting users tend to be more active in political communities, with their top three overlapping political subreddits ranking 19th, 23rd, and 32nd. Non-crime posting users' highest overlapping political communities rank 21st, 47th, and 77th.

\par From our user-level analysis, we have identified several characteristics of crime posters. First, these users are consistently more negative than non-crime posting users. They post about crime frequently, as indicated by their significant overlap with crime discussion specific communities. However, they are often somewhat local to the communities in which they post, as they have significant overlap to location specific hobby and sport communities. Despite this, crime posters have a smaller degree of overlap compared to non-crime posters. Lastly, those that post about crime are more active in conservative political communities than those who don't post about crime.

@@

\par Through analysis of user-submitted posts, we have found that communities that represent larger Metropolitan Statistical Areas and more liberal Metropolitan Statistical Areas tend to have higher rates of crime discussion. However, there is no correlation between high documented crime rates and high crime discussion rates. Furthermore, we have found that the users that make submissions about crime are significantly more negative in their posting and commenting style than those that post about non-crime topics. By measuring community overlap, we have found that these users are generally local to the communities they post in, although to a lesser degree than non-crime posters.
